\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage[]{hyperref}
\usepackage{fontspec} 
\addbibresource{bibliography.bib} % Specify the bibliography file to include publications
\geometry{a4paper}
\begin{document}

\header{Anand Chikkaballapur }{Umashankar}{Student at Sri Jayachamarajendra College Of Engineering} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
214 Abhyodaya Apartments
Dattagalli 3rd Stage
Somanthanagar
Mysore 570022
~
+91 9535629635
~
\href{mailto:anandcu3@gmail.com}{anandcu3@gmail.com}
\href{https://www.linkedin.com/in/anandcu3}{anandcu3@linkedin}
\section{Languages}
English 
Kannada (mother tongue)
Telugu
Hindi
\section{Programming}
{\color{black} $\varheartsuit$} Java \& PHP
C, Javascript \& AJAX 
CSS3 \& HTML5
\section{Frameworks and IDE's}
Android, SOAP \& REST Web Services, Eclipse, Android Studio, WEKA, 
\section{Web and Application Servers}
Apache Tomcat
\section{Databases}
MySQL, SQLite 
\section{General Computer Skills}
Knowledge of MS Word, Excel, Powerpoint 
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

\entry
{2006--Now}
{Bachelor {\normalfont of Computer Science \& Engineering}}
{Sri Jayachamarajendra College Of Engineering, Mysore}
{\emph{Major Subjects} \\ Data Structures, Analysis and Design of Algorithms, Database Management Systems, Computer Networks, Big Data, Web Technologies, Software Architecture, Programming in Java \newline}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Part Time}

\begin{entrylist}

\entry
{Jun-Oct 2015}
{EduSculpt Education Solutions}
{Chennai, India}
{\emph{Web Developer} \\
Complete design and development of the \href{http://www.edusculpt.com}{website} with the user interface. Creation and managing the database systems (MySQL). Backend for the website is primarily in PHP with the use of Ajax, Javascript with DOM and CSS for interactive UI. \newline}

%------------------------------------------------

\end{entrylist}

%\subsection{Full Time}

%\begin{entrylist}

%------------------------------------------------

%\entry
%{2010--2014}
%{Unisys Global Services India Limited}
%{Bangalore, India}
%{\emph{Software Developer and Consultant} \\
%\begin{itemize}
%\item Worked for LEIDA team (LEIDA - Library of Electronic Identification and Artifacts) responsible for the framework to enable biometric based access control and security solutions for Unisys.

%Projects :
%\begin{itemize}
%\item Department of Immigration and Citizenship (DIAC), Australia.  
%\item RND Project (Unisys America)
%\item ITER – International Thermonuclear Experimental Reactor, France.
%\end{itemize} 

%\item Work included development of Biometric Face, Finger and Iris Capture, Score and Quality Analysis modules. Integration of new biometric based search engines (1: N) and biometric based verification modules

%\item Work included development and integration of access control module to LEIDA framework.

%\item Knowledge of design workflows with JBPM5. Additional custom business rules implementation through Smooks framework and Groovy. 

%\end{itemize}}

%------------------------------------------------

%\end{entrylist}




%----------------------------------------------------------------------------------------
\section{Projects Undertaken}

\begin{entrylist}

%------------------------------------------------

\entry
{Jan-Apr 2015}
{Siblings Recognition}
{SJCE, Mysuru}
{Designed an algorithm for classifying a pair of images as sibling or not. The eigenfaces of both the images are extracted from the images and the pairs are compared using matrices evaluation using MATLAB and classification is done based on the confidence score.
\newline}

%------------------------------------------------

\entry
{Feb-Jun 2015}
{Real Estate Price Rediction}
{SJCE, Mysuru}
{Developed a tool to predict the real estate prices of the houses in major cities of India. Jaunt API is used scrape data from online retailers to create datasets for different cities. This data is then used for data mining using a tool called WEKA. Different algorithms are applied to find the most consistent algorithm across different datasets and is used for implementation. The tool was developed in Java and required the users to provide basic information about the house as input and the selling price is predicted as output. The tool also has an option to dynamically update the dataset used for training periodically and is completely portable.
\newline}

%------------------------------------------------

\entry
{Nov-Apr 2016}
{Hybrid Approach to Assess User Review}
{SJCE, Mysuru}
{
Implementation of semantic and machine learning approaches to analyse user reviews. Reviews for products which are trending are extracted using Jsoup from different E-commerce web sites and social networks. All the reviews for each product are processed to obtain a feature list for each product. This feature list is then used to convert the unstructured review dump into a dataset. The experiments consisted of two cases. The first case is classifying the reviews as spam or non spam based on the content and the rating in the review. The second case consisted of rating the review on a scale from 1 to 5. An android application was developed to help users access this work. The app helps users to access reliable reviews easily. A research paper titled "Hybrid Approach to Assess User Review" has been submitted to IMCIP Conference, Bangalore.
\newline}

%------------------------------------------------

\end{entrylist}
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards and Certifications}

\begin{entrylist}

%------------------------------------------------

\entry
{Feb'2016}
{Best Paper Presentation}
{St. Philomena's College, Mysuru}
{Awarded the best paper presentation in the field of machine learning during the National Conference on Emerging Trends in Computer Science and Technology for "Machine Learning Approach to Classify User Reviews".
\newline}

%------------------------------------------------

\entry
{Mar'2015}
{Presentation Certificate}
{Sunflower College Of Engineering and Technology, Vijayawada}
{Conducted a seminar on "Machine Learning Approach to Predict Real Estate Prices" in the International Conference on Computing, Communication, Electrical, Electronics, Devices \& Signal Processing.\newline  }

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{Communication skills}

%\begin{entrylist}

%------------------------------------------------

%\entry
%{2013-2014}
%{Oral Presentations}
%{Unisys Global Services India, Bangalore}
%{
%\begin{itemize}
%\item Conducted several presentations and trainings to team on the LEIDA framework in Unisys.
%\item Worked as Knowledge Management Champion for the team and organized training sessions and interacted with team to enable knowledge sharing, reducing dependencies among key members of teams. 
%\end{itemize}
%}


%------------------------------------------------

%\end{entrylist}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Publications}

\printbibsection{article}{Articles in international peer-reviewed journals} % Print all articles from the bibliography

%\printbibsection{book}{books} % Print all books %from the bibliography

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\begin{itemize}
\item \textbf{Professional:} machine learning, cloud computing, android development, research projects. 
\item \textbf{Personal:} football, trekking, music, novels, gadgets, gaming.\end{itemize}


%\begin{refsection} % This is a custom heading for %those references marked as "inproceedings" but not %containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, %type=inproceedings, title={international %peer-reviewed conferences/proceedings}, %notkeyword={france}, heading=bibheading]
%\end{refsection}
%
%\begin{refsection} % This is a custom heading for %those references marked as "inproceedings" and %containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, %type=inproceedings, title={local peer-reviewed %conferences/proceedings}, keyword={france}, %heading=bibheading]
%\end{refsection}

%\printbibsection{misc}{other publications} % Print %all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}